\documentclass[main.tex]{subfiles}

\begin{document}
\section*{Preface}
\subsection*{Brief presentation of the protocol}
GethDomains is a decentralized platform that allows, through the use of the GETH token, the purchase of Registered Domains on the Ethereum blockchain.\\
Our motto: discover the new, decentralized domain name system.


\subsection*{Team members and main responsibilities}
From the beginning, the whole team was working on the entire project, trying not to leave anything to chance and confronting themselves when problems or new ideas arise to be implemented or not.
Once the idea and the purpose of the project have been chosen, we have moved on to the definition of its architecture and then divided the work, always maintaining a synergy.
In particular:
\begin{itemize}
    \item Alessandro Scifoni: Smart Contract Developer, Pitch and Report, unit tester
    \item Simone Sestito: Flutter Web Developer, CI/CD pipeline, Web3.js integration
    \item Andrea Tarricone: Smart Contract Developer, Pitch and Report, Storytelling
\end{itemize}

\subsection*{Outline of the report}
Geth Domains is a decentralized platform that facilitates the association of TOR and IPFS addresses with more accessible domain names based on Ethereum. 
Based on blockchain, this system offers immutability and transparency of data, resistance to censorship and elimination of centralized intermediaries.
It leverages this blockchain technology to ensure the security and stability of domain names, allowing users to register them as NFT via the GETH token.
The platform includes a marketplace for buying and selling domains, giving users the chance to earn royalties for life when selling their domains.
Two distinct smart contracts, one for the token and one for the Dapp, work synergistically to support this ecosystem without the need for intermediaries. 

\end{document}